---
title: "serebiinet webscraping"
author: "Bram van Smoorenburg"
date: "1 August 2019"
output: html_document
---

https://www.db.yugioh-card.com/yugiohdb/card_search.action?ope=2&cid=4007

from 4007 to 14902

```{r}
library(rvest)
```

```{r}
no=6989
url=paste0("https://www.db.yugioh-card.com/yugiohdb/card_search.action?ope=2&cid=",no,collapse="")
#guess_encoding(url)
page=read_html(url,encoding = "ISO-8859-2")
page2=html_nodes(page,"table")
```

blue eyes white dragon:   4007
black luster soldier:     4370
maha vailo:               4499
pot of greed:             4844
winged dragon of ra:      5000
ring of destruction:      5005
dark master - zorc:       5782
elemental hero air neos:  6989
gaia knight, the force of earth:  7697
stardust dragon:          7734
number 39: utopia:        9576
gem-knight pearl:         9601
foucault's cannon:        11211
odd-eyes pendulum dragon: 11213
supreme king Z-ARC:       12953
firewall dragon:          13082
gaia saber, the lightning shadow: 13090

name
```{r}
name=as.character(html_nodes(page,"td")[[1]])
name=strsplit(name,"alt=")[[1]][2]
name=strsplit(name," title=")[[1]][1]
name=strsplit(name,NULL)[[1]]
name=paste0(name[-c(1,length(name))],collapse="")
if (name=="Search\">\n</td") {
  stop("hammertime")
}
```

load attributes
```{r}
page3=list()
for (i in 1:length(page2)) {page3[[i]]=try(html_table(page2[[i]],fill=TRUE))}
bla=page3[[2]]
bla2=apply(bla,c(1,2),function(x){gsub("\t","",x)})
bla2=apply(bla2,c(1,2),function(x){gsub("\r","",x)})
bla2=apply(bla2,c(1,2),function(x){gsub("\n","",x)})
```



write card data
```{r}
card=data.frame(dats=NULL)
if (nrow(bla2)==2) {
  tmp=strsplit(bla2[1,1]," Spell")[[1]]
  if (tmp!=bla2[1,1]) {
    cardtype="Spell"
  } else {
    cardtype="Trap"
    tmp=strsplit(bla2[1,1]," Trap")[[1]]
  }
  attribute=strsplit(tmp,"Icon")[[1]][2]
  extra=0
  type=NA
  level=NA
  ATK=NA
  DEF=NA
  effect=strsplit(bla2[2,1],"Card Text")[[1]][2]
  pendulumeffect=NA
  pendulumscale=NA
  linkarrows=NA
} else if (nrow(bla)==7) {
  tmp=strsplit(bla2[1,2],"Level")[[1]]
  if (length(tmp)==1) {
    tmp=strsplit(bla2[1,2],"Rank")[[1]]
    if (length(tmp)==1) {
      tmp=strsplit(bla2[1,2],"Link")
    }
  }
  level=as.numeric(tmp[2])
  cardtype=strsplit(bla2[5,1],"Card Type ")[[1]][2]
  extra=ifelse(gsub("Synchro","",cardtype)!=cardtype|gsub("Fusion","",cardtype)!=cardtype|gsub("Xyz","",cardtype)!=cardtype|gsub("Link","",cardtype)!=cardtype,1,0)
  attribute=strsplit(bla2[1,1],"Attribute")[[1]][2]
  type=strsplit(bla2[4,1],"Monster Type")[[1]][2]
  ATK=as.numeric(strsplit(bla2[6,1],"ATK")[[1]][2])
  DEF=as.numeric(strsplit(bla2[6,2],"DEF")[[1]][2])
  effect=strsplit(bla2[7,1],"Card Text")[[1]][2]
  pendulumeffect=strsplit(bla2[3,1],"Pendulum Effect")[[1]][2]
  pendulumscale=as.numeric(strsplit(bla2[2,1],"Pendulum Scale")[[1]][2])
  linkarrows=NA
} else {
  tmp=strsplit(bla2[1,2],"Level")[[1]]
  if (length(tmp)==1) {
    tmp=strsplit(bla2[1,2],"Rank")[[1]]
    if (length(tmp)==1) {
      tmp=strsplit(bla2[1,2],"Link")
    }
  }
  level=as.numeric(tmp[2])
  cardtype=strsplit(bla2[3,1],"Card Type ")[[1]][2]
  extra=ifelse(gsub("Synchro","",cardtype)!=cardtype|gsub("Fusion","",cardtype)!=cardtype|gsub("Xyz","",cardtype)!=cardtype|gsub("Link","",cardtype)!=cardtype,1,0)
  attribute=strsplit(bla2[1,1],"Attribute")[[1]][2]
  type=strsplit(bla2[2,1],"Monster Type")[[1]][2]
  ATK=as.numeric(strsplit(bla2[4,1],"ATK")[[1]][2])
  DEF=as.numeric(strsplit(bla2[4,2],"DEF")[[1]][2])
  effect=strsplit(bla2[5,1],"Card Text")[[1]][2]
  pendulumeffect=NA
  pendulumscale=NA
  linkarrows=NA
}
data.frame(extra,name,cardtype,attribute,type,level,ATK,DEF,effect,pendulumeffect,pendulumscale,linkarrows)
```

loop
```{r}
cards=data.frame(Name=NA,Cardtype=NA,Attribute=NA,Type=NA,Level=NA,ATK=NA,DEF=NA,Effect=NA,Pendulumeffect=NA,Pendulumscale=NA,Linkarrows=NA)[-1,]
for (i in 4007:14902) {
  url=paste0("https://www.db.yugioh-card.com/yugiohdb/card_search.action?ope=2&cid=",i,collapse="")
  page=try(read_html(url,encoding = "ISO-8859-2"))
  if (all(class(page)=="try-error")) {
    page=read_html(url,encoding = "ISO-8859-2")
  }
  name=as.character(html_nodes(page,"td")[[1]])
  name=strsplit(name,"alt=")[[1]][2]
  name=strsplit(name," title=")[[1]][1]
  name=strsplit(name,NULL)[[1]]
  name=paste0(name[-c(1,length(name))],collapse="")
  if (name=="Search\">\n</td") {
    next
  }
  
  page2=html_nodes(page,"table")
  page3=list()
  for (s in 1:length(page2)) {page3[[s]]=try(html_table(page2[[s]],fill=TRUE))}
  bla=page3[[2]]
  bla2=apply(bla,c(1,2),function(x){gsub("\t","",x)})
  bla2=apply(bla2,c(1,2),function(x){gsub("\r","",x)})
  bla2=apply(bla2,c(1,2),function(x){gsub("\n","",x)})
  
  if (nrow(bla2)==2) {
    tmp=strsplit(bla2[1,1]," Spell")[[1]]
    if (tmp!=bla2[1,1]) {
      cardtype="Spell"
    } else {
      cardtype="Trap"
      tmp=strsplit(bla2[1,1]," Trap")[[1]]
    }
    attribute=strsplit(tmp,"Icon")[[1]][2]
    extra=0
    type=NA
    level=NA
    ATK=NA
    DEF=NA
    effect=strsplit(bla2[2,1],"Card Text")[[1]][2]
    pendulumeffect=NA
    pendulumscale=NA
    linkarrows=NA
  } else if (nrow(bla)==7) {
    tmp=strsplit(bla2[1,2],"Level")[[1]]
    if (length(tmp)==1) {
      tmp=strsplit(bla2[1,2],"Rank")[[1]]
      if (length(tmp)==1) {
        tmp=strsplit(bla2[1,2],"Link")
      }
    }
    level=as.numeric(tmp[2])
    cardtype=strsplit(bla2[5,1],"Card Type ")[[1]][2]
    extra=ifelse(gsub("Synchro","",cardtype)!=cardtype|gsub("Fusion","",cardtype)!=cardtype|gsub("Xyz","",cardtype)!=cardtype|gsub("Link","",cardtype)!=cardtype,1,0)
    attribute=strsplit(bla2[1,1],"Attribute")[[1]][2]
    type=strsplit(bla2[4,1],"Monster Type")[[1]][2]
    ATK=as.numeric(strsplit(bla2[6,1],"ATK")[[1]][2])
    DEF=as.numeric(strsplit(bla2[6,2],"DEF")[[1]][2])
    effect=strsplit(bla2[7,1],"Card Text")[[1]][2]
    pendulumeffect=strsplit(bla2[3,1],"Pendulum Effect")[[1]][2]
    pendulumscale=as.numeric(strsplit(bla2[2,1],"Pendulum Scale")[[1]][2])
    linkarrows=NA
  } else {
    tmp=strsplit(bla2[1,2],"Level")[[1]]
    if (length(tmp)==1) {
      tmp=strsplit(bla2[1,2],"Rank")[[1]]
      if (length(tmp)==1) {
        tmp=strsplit(bla2[1,2],"Link")[[1]]
      }
    }
    level=as.numeric(tmp[2])
    cardtype=strsplit(bla2[3,1],"Card Type ")[[1]][2]
    extra=ifelse(gsub("Synchro","",cardtype)!=cardtype|gsub("Fusion","",cardtype)!=cardtype|gsub("Xyz","",cardtype)!=cardtype|gsub("Link","",cardtype)!=cardtype,1,0)
    attribute=strsplit(bla2[1,1],"Attribute")[[1]][2]
    type=strsplit(bla2[2,1],"Monster Type")[[1]][2]
    ATK=suppressWarnings(as.numeric(strsplit(bla2[4,1],"ATK")[[1]][2]))
    DEF=suppressWarnings(as.numeric(strsplit(bla2[4,2],"DEF")[[1]][2]))
    effect=strsplit(bla2[5,1],"Card Text")[[1]][2]
    pendulumeffect=NA
    pendulumscale=NA
    linkarrows=NA
  }
  
  cards=rbind(cards,data.frame(extra,name,cardtype,attribute,type,level,ATK,DEF,effect,pendulumeffect,pendulumscale,linkarrows))
  
  print(c(i,name))
}
```
